---
title: "cust"
output: html_document
date: "2026-03-09"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## R Markdown
# Load required libraries
```{r}
library(dplyr)
# Read dataset
data <- read.csv("C:/Users/teaga/Downloads/star_digital.csv")

```
# Check structure
```{r}
str(data)
summary(data)
#Question 1) Is online advertising effective? (Treatment vs Control)
#A Conversion Rate Comparison
data %>%
  group_by(test) %>%
  summarise(
    conversion_rate = mean(purchase),
    count = n()
  )
#B Difference in Means Test
t.test(purchase ~ test, data = data)
#C Logistic Regression (Causal Effect)
model_q1 <- glm(purchase ~ test, data = data, family = binomial)
summary(model_q1)
# Odds ratios
exp(coef(model_q1))
```
#Final answer>> Online advertising appears to have a positive effect on purchase behavior, 
increasing conversion rates by about 1.9 percentage points. However, the evidence is only 
marginally significant, so the effectiveness of advertising is suggestive rather than 
strongly conclusive.
#Question 2: Is there a frequency effect?
#A Create Total Impressions Variable
```{r}
data$total_impressions <- rowSums(data[, 
c("imp_1","imp_2","imp_3","imp_4","imp_5","imp_6")])
#B Logistic Regression with Frequency
model_q2 <- glm(purchase ~ total_impressions, 
                data = data, 
                family = binomial)
summary(model_q2)
exp(coef(model_q2))
#C Optional: Diminishing Returns Test
data$total_impressions_sq <- data$total_impressions^2
model_q2_quad <- glm(purchase ~ total_impressions + total_impressions_sq,
                     data = data,
                     family = binomial)
summary(model_q2_quad)
```
#Question 3: Compare Sites 1–5 vs Site 6
#We compare effectiveness using impressions separately.
```{r}
model_q3 <- glm(purchase ~ imp_1 + imp_2 + imp_3 + imp_4 + imp_5 + imp_6,
                data = data,
                family = binomial)
summary(model_q3)
exp(coef(model_q3))
```
#Compared to most of Sites 1–5, Site 6 performs better than Sites 1, 3, and 5. However, 
Site 4 clearly outperforms Site 6 by a substantial margin.
#Question 4: Where should Star Digital allocate budget?
#Compare Combined Sites 1–5 vs Site 6
```{r}
data$imp_1_5 <- rowSums(data[, c("imp_1","imp_2","imp_3","imp_4","imp_5")])
model_q4 <- glm(purchase ~ imp_1_5 + imp_6,
                data = data,
                family = binomial)
summary(model_q4)
exp(coef(model_q4))

#Predicted Probability Comparison
data$predicted_prob <- predict(model_q4, type = "response")
mean(data$predicted_prob)
```
#While both advertising channels are effective, Sites 1–5 collectively produce a larger 
marginal return per impression than Site 6. Therefore, Star Digital should allocate a 
greater share of its advertising budget to Sites 1–5, with emphasis on the highest 
performing site within that group.
library(ggplot2)
#Question 1 visual
# Conversion rate by treatment
```{r}
install.packages("ggplot2")
library(ggplot2)
conv_data <- data %>%
  group_by(test) %>%
  summarise(conversion_rate = mean(purchase))
ggplot(conv_data, aes(x = factor(test), y = conversion_rate, fill = factor(test))) +
  geom_bar(stat = "identity") + geom_text(aes(y = conversion_rate / 2,
                label = round(conversion_rate, 3)),
            color = "white",
            size = 5) +
  labs(
    title = "Conversion Rate: Treatment vs Control",
    x = "Group (0 = Control, 1 = Treatment)",
    y = "Conversion Rate"
  ) +
  theme_minimal() +
  guides(fill = "none")
#Question 2 Visual
# Create prediction grid
new_data <- data.frame(
  total_impressions = seq(0, max(data$total_impressions), length.out = 100)
)
new_data$total_impressions_sq <- new_data$total_impressions^2
new_data$predicted_prob <- predict(model_q2_quad, 
                                   newdata = new_data, 
                                   type = "response")
ggplot(new_data, aes(x = total_impressions, y = predicted_prob)) +
  geom_line(size = 1) +
  labs(
    title = "Effect of Advertising Frequency on Purchase Probability",
    x = "Total Impressions",
    y = "Predicted Purchase Probability"
  ) +
  theme_minimal()
#Question 3 visual 
# Extract odds ratios
odds_ratios <- exp(coef(model_q3))[-1]
site_data <- data.frame(
  site = names(odds_ratios),
  odds_ratio = odds_ratios
)
ggplot(site_data, aes(x = site, y = odds_ratio)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  geom_hline(yintercept = 1, linetype = "dashed", color = "red") +
  labs(
    title = "Effectiveness by Site (Odds Ratios)",
    x = "Site",
    y = "Odds Ratio"
  ) +
  theme_minimal()
#Question 4 visual
budget_odds <- exp(coef(model_q4))[-1]
budget_data <- data.frame(
  channel = names(budget_odds),
  odds_ratio = budget_odds
)
ggplot(budget_data, aes(x = channel, y = odds_ratio)) +
  geom_bar(stat = "identity", fill = "darkgreen") +     geom_text(aes(y = odds_ratio / 2, label = round(odds_ratio, 4)),
            color = "white",
            size = 5)+
  geom_hline(yintercept = 1, linetype = "dashed", color = "red") +
  labs(
    title = "Budget Allocation Impact Comparison",
    x = "Channel",
    y = "Odds Ratio"
  ) +
  theme_minimal()
```
```{r}
data$imp_1_5 <- rowSums(data[, c("imp_1","imp_2","imp_3","imp_4","imp_5")], na.rm = TRUE)

model_q4 <- glm(purchase ~ imp_1_5 + imp_6, data = data, family = binomial)

summary(model_q4)
exp(coef(model_q4))
b1 <- coef(model_q4)["imp_1_5"]
b2 <- coef(model_q4)["imp_6"]

imp_1_5_for_100 <- (100 / 25) * 1000
imp_6_for_100   <- (100 / 20) * 1000

exp(imp_1_5_for_100 * b1)
exp(imp_6_for_100 * b2)

(exp(imp_1_5_for_100 * b1) - 1) * 100
(exp(imp_6_for_100 * b2) - 1) * 100
```

```{r}
# Question 2 Visual
# Create prediction grid
new_data <- data.frame(
  total_impressions = seq(0, max(data$total_impressions), length.out = 100)
)

new_data$total_impressions_sq <- new_data$total_impressions^2
new_data$predicted_prob <- predict(
  model_q2_quad,
  newdata = new_data,
  type = "response"
)

# Find turning point
turn_point <- new_data[which.max(new_data$predicted_prob), ]

ggplot(new_data, aes(x = total_impressions, y = predicted_prob)) +
  geom_line(linewidth = 1) +
  geom_point(data = turn_point,
             aes(x = total_impressions, y = predicted_prob),
             color = "red",
             size = 3) +
  geom_text(data = turn_point,
            aes(x = total_impressions,
                y = predicted_prob,
                label = round(total_impressions, 1)),
            color = "black",
            vjust = 2,
            size = 5) +
  labs(
    title = "Effect of Advertising Frequency on Purchase Probability",
    x = "Total Impressions",
    y = "Predicted Purchase Probability"
  ) +
  theme_minimal()
```
```{r}
# ROI


# 1) Load data
data <- read.csv("star_digital (2).csv")

# Check purchase rate in analysis sample
mean(data$purchase)   # should be around 0.50


# 2) Build variables
# Total impressions across sites 1-5
data$imp_1_5 <- rowSums(data[, c("imp_1", "imp_2", "imp_3", "imp_4", "imp_5")], na.rm = TRUE)

# Showing effect = at least one impression
data$show_1_5 <- ifelse(data$imp_1_5 > 0, 1, 0)
data$show_6   <- ifelse(data$imp_6 > 0, 1, 0)

# Frequency effect = extra impressions after the first
data$freq_1_5 <- pmax(data$imp_1_5 - 1, 0)
data$freq_6   <- pmax(data$imp_6 - 1, 0)


# 3) Fit model on SAMPLE scale

# No offset here
# The causal ad effect is identified by interactions with test
model <- glm(
  purchase ~ test +
    show_1_5 + freq_1_5 + show_6 + freq_6 +
    test:show_1_5 + test:freq_1_5 +
    test:show_6   + test:freq_6,
  family = binomial(link = "logit"),
  data = data
)

summary(model)
exp(coef(model))   # odds ratios


# 4) Offset to true population conversion rate

# True conversion rate = 0.153% = 0.00153
true_purchase_rate   <- 0.00153
sample_purchase_rate <- mean(data$purchase)

offset_factor <- qlogis(true_purchase_rate) - qlogis(sample_purchase_rate)
offset_factor


# 5) Predicted probabilities on POPULATION scale

# First get sample-scale linear predictor
lp_sample <- predict(model, type = "link")

# Then shift to population-scale with offset
lp_pop <- lp_sample + offset_factor
p_full <- plogis(lp_pop)

summary(p_full)
mean(p_full)   # should now be small, near real-world scale


# 6) Counterfactual: remove Site 6 causal effect

b <- coef(model)

lp_no6_sample <- lp_sample -
  b["test:show_6"] * (data$test * data$show_6) -
  b["test:freq_6"] * (data$test * data$freq_6)

lp_no6_pop <- lp_no6_sample + offset_factor
p_no6 <- plogis(lp_no6_pop)

inc_conv_6 <- sum(p_full - p_no6)
inc_conv_6


# 7) Counterfactual: remove Sites 1-5 causal effect

lp_no15_sample <- lp_sample -
  b["test:show_1_5"] * (data$test * data$show_1_5) -
  b["test:freq_1_5"] * (data$test * data$freq_1_5)

lp_no15_pop <- lp_no15_sample + offset_factor
p_no15 <- plogis(lp_no15_pop)

inc_conv_15 <- sum(p_full - p_no15)
inc_conv_15

# 8) Impression totals and costs

# Only treated users got Star Digital ads
imps_15 <- sum(data$imp_1_5[data$test == 1], na.rm = TRUE)
imps_6  <- sum(data$imp_6[data$test == 1], na.rm = TRUE)

cpm_15 <- 25
cpm_6  <- 20

cost_15 <- (imps_15 / 1000) * cpm_15
cost_6  <- (imps_6  / 1000) * cpm_6

cost_15
cost_6


# 9) Revenue and ROI

purchase_value <- 1200

rev_15 <- inc_conv_15 * purchase_value
rev_6  <- inc_conv_6  * purchase_value

roi_15 <- (rev_15 - cost_15) / cost_15
roi_6  <- (rev_6  - cost_6) / cost_6

roi_15
roi_6


# 10) Incremental revenue per 1000 impressions

inc_rev_per_1000_15 <- (inc_conv_15 / imps_15) * 1000 * purchase_value
inc_rev_per_1000_6  <- (inc_conv_6  / imps_6 ) * 1000 * purchase_value

inc_rev_per_1000_15
inc_rev_per_1000_6

# Break-even check
# Profitable if incremental revenue per 1000 impressions > CPM
inc_rev_per_1000_15 - cpm_15
inc_rev_per_1000_6  - cpm_6


# 11) Results table

results <- data.frame(
  Option = c("Sites 1-5", "Site 6"),
  Impressions = c(imps_15, imps_6),
  Cost = c(cost_15, cost_6),
  Incremental_Conversions = c(inc_conv_15, inc_conv_6),
  Incremental_Revenue = c(rev_15, rev_6),
  ROI = c(roi_15, roi_6)
)

print(results)


# 12) Recommendation

if (roi_6 > roi_15) {
  cat("\nRecommendation: Site 6 has the higher estimated ROI.\n")
} else {
  cat("\nRecommendation: Sites 1-5 have the higher estimated ROI.\n")
}

if (inc_rev_per_1000_6 > cpm_6) {
  cat("Site 6 appears profitable on an incremental basis.\n")
} else {
  cat("Site 6 does NOT appear profitable on an incremental basis.\n")
}

if (inc_rev_per_1000_15 > cpm_15) {
  cat("Sites 1-5 appear profitable on an incremental basis.\n")
} else {
  cat("Sites 1-5 do NOT appear profitable on an incremental basis.\n")
}


# 13) Helpful diagnostics

cat("\n--- Diagnostics ---\n")
cat("Sample purchase rate: ", sample_purchase_rate, "\n")
cat("True purchase rate:   ", true_purchase_rate, "\n")
cat("Offset factor:        ", offset_factor, "\n")
cat("Mean predicted probability (population scale): ", mean(p_full), "\n")
```

```{r}
roi_15
roi_6
```
`
```{r}
model
```

